---
title: "Original Analysis"
date: "5/3/2021"
output: word_document
---
### We would like to determine significant predictors for tumor Class (whether it has shown recurrence or no recurrence) based on the covariates within the dataset using logistic regression ### 

##Load Dataset 
```{r}
#install.packages("jsonlite", repos="https://cran.rstudio.com/")
library("jsonlite")
library(dplyr)
library(mlbench)

json_file <- 'https://datahub.io/machine-learning/breast-cancer/datapackage.json'
json_data <- fromJSON(paste(readLines(json_file), collapse=""))

# get list of all resources:
print(json_data$resources$name)

# print all tabular data(if exists any)
for(i in 1:length(json_data$resources$datahub$type)){
  if(json_data$resources$datahub$type[i]=='derived/csv'){
    path_to_file = json_data$resources$path[i]
    data <- read.csv(url(path_to_file))
    print(data)
  }
}
data<-data[sample(1:nrow(data)),]
drop<-c(150, 93, 51, 265, 55, 32, 72, 241)
drop<-as.integer(drop)
data <- data[-drop, ]                                            #drop NA rows 
#columns numbers 1 through 11, convert to numeric 
#cols<-c(1:9) 
#data[cols]<-sapply(data[cols], as.numeric) #results in 'NAs introduced by coercion' 
#convert type to factor  
data$Class<-factor(data$Class) 
head(data)
```
#logistic regression 
```{r}
#logistic regression model with all 9 covariates 
model <- glm(Class ~ .,family = binomial(logit), data=data)
summary(model)

#coeffecients of covariates 
exp(model$coefficients)
```
##The most significant predictor of whether a tumor is characterized by recurrence or non-reucrrence is deg.malig. Based on the fitted model deg.malig has a small p-value of 0.00492 (p-value < 0.05) making it an significant covariate in making accurate predictions of tumor Class. Based on the covariate coeffecients, for a unit increase in deg.malig the odds of the tumor being characterized by reccurence increased by 1.939000e+00. 

#AIC selection  
```{r}
library(MASS)
#step AIC selection starting with all 9 covariates 
summary(stepAIC(model, direction="backward"))
```
#Based on the AIC selection node.capsno, node.capsyes, deg.malig are good indicators of tumor Class, however accprding to p-value deg.malig is still the most significant predictor of reccurence and non-recurrence

#reduced logistic regression
```{r}
#reduced model with significant covariates (deg.malig)
reducedmodel<- glm(Class ~ deg.malig,family = binomial(logit), data=data)

exp(reducedmodel$coefficients)
```

#k-fold cross validation
```{r}
#fit reduced model on training set + k-fold cross validation 
library(caret)
set.seed(125)

Train <- createDataPartition(data$Class, p=0.75, list=FALSE)
training <- data[ Train, ]
testing <- data[ -Train, ]

train.control<-trainControl(method = "repeatedcv", number = 10, savePredictions = TRUE, repeats = 5)

training$Class<-factor(training$Class) 

cvmodel <- train(Class ~ deg.malig, data = training, trControl = train.control, method = "glm", family = "binomial")

print(cvmodel)

```
#The accuraccy of the fitted model is 68.39% which means the model does not always provide dependable and accurate predictions for tumor class. Further analysis or different training methods could be used in creating a better fitted model or re-assessing significance of covariates.  

